My title

### 2024-02-15 outputs/paper/paper.qmd
change ref

## Data Measurements
The measurement of bullying from Google Trends is the search intensity of keywords, which are published every month [@citePaper]. Search intensity stands for the fraction of a given area’s Google searches for a specific topic. Google Trends normalizes the search intensity numbers to get relative intensity over time and across states. The search intensity is measured on a scale of 0 to 100, where 0 represents the lowest search intensity and 100 the highest.

@@

## Features
The original dataset contained 5 variables, which are named as “dma_json_code”, “date”, “keyword”, “hits”, and “ratio”. 
1. dma_json_code: the states of the United States
2. date: the first day of every month from 2012. 01 to 2021. 02
3. keyword: specific words that the people search on Google Trends that relate to bullying.
4. hits: number of searchers of keywords in each month.
5. ratio:

@@

It is clear that the incidence of school bullying has generally been decreasing over time. The original paper (@citePaper) states that COVID-19 pandemic and remote learning has caused a decrease in school bullying cases. Our data has a slight different conclusion compared to the original paper (@fig-Composite-Search-Intensity-bully). It is observed that with the sudden COVID-19 outbreak in the United States around January 2020, instances of school bullying experienced a notable surge, almost reaching global maxima in February 2020. The unexpected rise in bullying during the pandemic could be attributed to various factors, for example, individuals seeking to alleviate stress through harmful behavior to other people. Furthermore, a disturbing trend of Chinese-hate emerged during this period, due to the misguided assumptions that China was responsible for spreading the virus (@citeChineseHate). Asian students, especially Chinese ethnicity, might experience discriminatory actions, verbal abuse, or physical assaults due to this misinformation. So it most likely contributed to an increase in school bullying cases. As schools closed down in February 2020, a consequential decline in bullying cases was observed, at times nearly reaching zero. This is understandable since student interactions have declined due to remote learning. They did not have  as much opportunity or motivation to bully others as they had before.

>>>>

## Data Measurements
The measurement of bullying from Google Trends is the search intensity of keywords, which are published every month (@citePaper). Search intensity stands for the fraction of a given area’s Google searches for a specific topic. Google Trends normalizes the search intensity numbers to get relative intensity over time and across states. The search intensity is measured on a scale of 0 to 100, where 0 represents the lowest search intensity and 100 the highest.

@@

## Features
The original dataset contained 5 variables, which are named as “dma_json_code”, “date”, “keyword”, “hits”, and “ratio”.

1. dma_json_code: the states of the United States.

2. date: the first day of every month from January 2012 to February 2021.

3. keyword: specific words that the people search on Google Trends that relate to bullying.

4. hits: number of searchers of keywords in each month.

5. ratio: ratio of the search intensity in Google Trend.

@@

It is clear that the incidence of school bullying has generally been decreasing over time. The original paper (@citePaper) states that COVID-19 pandemic and remote learning has caused a decrease in school bullying cases. Our data has a slight different conclusion compared to the original paper (@fig-Composite-Search-Intensity-bully, @fig-Composite-Search-Intensity-sch, @fig-Composite-Search-Intensity-cyber). It is observed that with the sudden COVID-19 outbreak in the United States around January 2020, instances of school bullying experienced a notable surge, almost reaching global maxima in February 2020. The unexpected rise in bullying during the pandemic could be attributed to various factors, for example, individuals seeking to alleviate stress through harmful behavior to other people. Furthermore, a disturbing trend of Chinese-hate emerged during this period, due to the misguided assumptions that China was responsible for spreading the virus (@citeChineseHate). Asian students, especially Chinese ethnicity, might experience discriminatory actions, verbal abuse, or physical assaults due to this misinformation. So it most likely contributed to an increase in school bullying cases. As schools closed down in February 2020, a consequential decline in bullying cases was observed, at times nearly reaching zero. This is understandable since student interactions have declined due to remote learning. They did not have  as much opportunity or motivation to bully others as they had before.
